Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2014-10-19 Report/kkt_mse_approach.tex
update final draft

The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive precoders \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s corresponding to precoder weights are initialized with ones to have equal weights. The transmit precoders in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}. Following approaches can be performed to decouple the precoder design problem with the limited signaling between the \acp{BS} in \me{\mathcal{B}}.

As a first approach, in this method, for a fixed the receive beamformers, \me{\alpha_{l,k,n}} and the operating \ac{SCA} point \me{\tilde{\epsilon}_{l,k,n}}, each \ac{BS} evaluates the transmit precoder \me{\mvec{m}{l,k,n}^{(i)}} and exchange the total interference contribution by using the updated precoder to the neighboring \ac{BS} users. On receiving this information, each \ac{BS} will update \eqref{kkt-mse-4.4}, \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2}, and \eqref{kkt-mse-4.1}. For the fixed receive beamformer, the dual variables \me{\alpha_{l,k,n}} and the interference contributions are exchanged until convergence by finding the updated transmit precoders. Once the dual variables are converged, the receivers are updated by performing the downlink transmission. This procedure is iterated until convergence for a fixed \me{I_{\max}} iterations. The convergence is similar to the \ac{JSFRA} scheme with \ac{MSE} reformulation in Section \ref{sec-3.3}.

The following approaches are similar to the decentralization methods proposed in \cite{komulainen2013effective} for the sum rate maximization problem. In the this approach, after receiving the transmitted signal with the recent precoders from all \acp{BS} in \me{\mathcal{B}}, the users evaluate the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify it to the \acp{BS} using the precoded uplink pilots. Upon receiving, each \ac{BS} estimates the \ac{MSE} using \me{\epsilon_{l,k,n}^{(i)} = 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)}}. Using the updated \ac{MSE}, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}. The updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration.

Finally, in this approach, upon receiving the signal from all \acp{BS}, the users update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}. The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified the \acp{BS} using precoded uplink pilots with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{\bar{w}}{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders. On receiving the precoded uplink pilots, the \acp{BS} will use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}. Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem.

>>>>

The \ac{KKT} expressions in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the transmit and the receive beamformers \me{\mvec{M}{k,n},\mvec{W}{k,n}} with the single user beamforming and the \ac{MMSE} vectors. The dual variable \me{\alpha}'s are initialized with ones to have equal priorities to the corresponding precoders. Using this, the transmit and the receive beamformers are evaluated using the expressions in \eqref{kkt-mse-4}. The transmit precoder in \eqref{kkt-mse-4.3} depends on the \ac{BS} specific dual variable \me{\delta_b}, which can be found by bisection method satisfying the total power constraint \eqref{kkt-mse-1.4}. Note that in \eqref{kkt-mse-4}, the fixed \ac{SCA} operating point is given by \me{\tilde{\epsilon}_{l,k,n} = \epsilon_{l,k,n}^{(i-1)}}. As discussed in Section \ref{sec-4.1}, the \ac{KKT} expressions can be solved in a distributed manner using primal method with similar convergence behavior.

We extend the decentralization methods discussed in \cite{komulainen2013effective}, for the problem of minimizing the total number of backlogged packets. After receiving the updated transmit precoders from all \acp{BS} in \me{\mathcal{B}}, each user evaluates the \ac{MMSE} receiver in \eqref{kkt-mse-4.6} and notify them to the \acp{BS} via uplink precoded pilots. On receiving pilot signals, \acp{BS} update the \ac{MSE} as 
\begin{equation}
\epsilon_{l,k,n}^{(i)} = \Re{ \lbrace 1 - \mvec{w}{l,k,n}^{(i)\herm} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \rbrace }.
\end{equation}
Using the current \ac{MSE}, \me{t_{l,k,n}^{(i)},\sigma_{l,k,n}^{(i)}}, and \me{\alpha_{l,k,n}^{(i)}} are evaluated using \eqref{kkt-mse-4.5}, \eqref{kkt-mse-4.2} and \eqref{kkt-mse-4.1}. The updated dual variables \me{\alpha_{l,k,n}} are exchanged between the \acp{BS} to evaluate the transmit precoders \me{\mvec{m}{l,k,n}^{(i+1)}} for the next iteration. The \ac{SCA} operating point is also updated with the current \ac{MSE} value.

In order to limit the back-haul exchanges between \acp{BS}, in this approach, users will perform all processing required and \acp{BS} will update the precoders based on the feedback information from the users. Upon receiving the transmit precoders from \acp{BS}, each user will update the receive beamformer \me{\mvec{w}{l,k,n}}, the \ac{MSE} \me{\epsilon_{l,k,n}}, and the dual variables \me{\lambda_{l,k,n}} and \me{\alpha_{l,k,n}}. The updated \me{\alpha_{l,k,n}} and \me{\mvec{w}{l,k,n}} are notified to the \acp{BS} using two separate precoded uplink pilot symbols with \me{\mvec{\tilde{w}}{l,k,n}^{(i)} = \sqrt{\alpha_{l,k,n}^{(i)}}\mvec{w}{l,k,n}^{\ast(i)}} and \me{\mvec{\bar{w}}{l,k,n}^{(i)} = \alpha_{l,k,n}^{(i)}\mvec{w}{l,k,n}^{\ast(i)}} as the precoders. On receiving the precoded uplink pilots, each \ac{BS} use the effective channel \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{\tilde{w}}{l,k,n}^{(i)}} and \me{\mvec{H}{b,k,n}^{\mathrm{T}} \mvec{w}{l,k,n}^{(i)}} in \eqref{kkt-mse-4.3} to update the transmit precoders, where \me{\mbf{x}^{\ast}} is the complex conjugate of \me{\mbf{x}}. Algorithm \ref{algo-4} outlines the distributed precoder design using the \ac{KKT} based \ac{MSE} reformulated \ac{JSFRA} problem. The proposed scheme in Algorithm \ref{algo-4} is of practical importance due to low signaling requirements. The convergence proof for the \ac{MSE}-\ac{KKT} schemes are difficult due to the joint update of \me{\mvec{w}{l,k,n}} and the \ac{SCA} update \me{\tilde{\epsilon}_{l,k,n}}. It is verified for various exponent values by using numerical simulations.
